Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-06-16 arxiv/template.tex
include string

>>>>

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[width=7cm]{light_start_at_r_equals_2.pdf} }}%
    \subfloat{{\includegraphics[width=7cm]{light_start_at_r_equals_2_stringcoords.pdf} }}
    \caption{Null geodesics near a black hole.  Left, diagram using $r,\phi$
      coordinates.  Right, same spacetime but presented in $u_1,\phi$
      coordinates: note absence of interior on right}
    \label{light_2}%
\end{figure}

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[width=7cm]{light_closest_approach.pdf} }}%
    \subfloat{{\includegraphics[width=7cm]{light_closest_approach_stringcoords.pdf} }}
    \caption{Null geodesics near a black hole.  Left, diagram using $r,\phi$
      coordinates.  Right, same spacetime but presented in $u_1,\phi$
      coordinates: note absence of interior on right}
    \label{light_closest_2}%
\end{figure}

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[width=7cm]{closest_approach_nonselfintersecting.pdf} }}%
    \subfloat{{\includegraphics[width=7cm]{closest_approach_nonselfintersecting_stringcoords.pdf} }}
    \caption{Light inextensible string near a black hole,
      non-self-intersecting case.  Left, diagram using $r,\phi$
      coordinates.  Right, same spacetime but presented in $u_1,\phi$
      coordinates: note absence of interior on right}
    \label{closest_approach_nonself}%
\end{figure}

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[width=7cm]{closest_approach_selfintersecting.pdf} }}%
    \subfloat{{\includegraphics[width=7cm]{closest_approach_selfintersecting_stringcoords.pdf} }}
    \caption{Light inextensible string near a black hole, self intersecting case.  Left, diagram using $r,\phi$
      coordinates.  Right, same spacetime but presented in $u_1,\phi$
      coordinates: note absence of interior on right}
    \label{closest_approach_self}%
\end{figure}
